% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\section{Matthew Mayers}\label{matthew-mayers}

Software engineer with over a decade of experience across mobile
development, web development, and systems administration.

San Francisco, CA\\
mmayers at gmail.com

\subsection{Experience}\label{experience}

\textbf{Google}\\
Software Engineer, L5\\
San Francisco, CA\\
February 2021 - Present

In addition to continuing pre-aquisition Fitbit work, I also went on to
contribute to Health and Fitness features on the Pixel watch. Most
recently, I worked on a data sync pipeline for two-way data sync between
Health Connect and the Fitbit app.

\textbf{Fitbit (acquired by Google)}\\
Senior Software Engineer\\
San Francisco, CA\\
March 2019 - February 2021

Led development of several core features of the Fitbit Android app,
including: Sleep Score; Menstrual Health; Mindfulness. Supported
development of regulated features requiring strong compliance with FDA
rules.

\textbf{Branch Messenger}\\
Android Lead\\
San Francisco, CA\\
December 2017 - February 2019

As Android lead, I was responsible for designing app architecture,
development workflow, and building automated build, test, and deployment
processes.

\textbf{Quizlet}\\
Software Engineer\\
San Francisco, CA\\
March 2017 - September 2017

As a member of Quizlet's Android team, I was responsible for
implementing new study modes and features to help students get an edge
in their classes.

\textbf{Oneteam, Inc.}\\
Android Lead\\
Tokyo, Japan\\
March 2016 - March 2017

This position started out as a part-time remote role before
transitioning to full-time onsite. I was responsible for designing the
architecture for Oneteam's mobile app and leading the project from the
ground up.

\textbf{8tracks}\\
Android Lead\\
San Francisco, CA\\
January 2015 - September 2016

As the sole fulltime Android developer, I was responsible for making
major architecture and design decisions for the app and its features. I
also was responsible for building in support for both direct sale ads
and ads provided by mediation networks to maximize mobile revenue.

\textbf{Wink, Inc.}\\
Android Engineer\\
San Francisco, CA\\
January 2014 - December 2014

As an Android engineer, I was responsibile for new feature development
and building support into the Wink mobile app for various connected home
devices manufactured by partner companies.

\textbf{HotelTonight}\\
Android Engineer\\
San Francisco, CA\\
June 2012 - December 2013

Working on HotelTonight's Android team, my duties consisted of fixing
bugs, implementing new features, and keeping the UX and functionality in
line with both HotelTonight's brand standards and the usability patterns
expected by Android users.

\textbf{Electronic Arts/Playfish}\\
Devops Contractor\\
San Francisco, CA\\
April 2012 - June 2012

In this short-term contract position I assisted in the deployment of
EA/Playfish games, troubleshooting of server infrastructure, and the
development of data visualization solutions for infrastructure metrics.

\textbf{Own Point of Sale}\\
Senior Engineer/Systems Architect\\
San Francisco, CA\\
May 2011 - March 2012

As System Architect, it was my responsibility to design, document, and
implement scalable solutions for both new features and problems created
by a legacy codebase. This also involved a lot of architecture design
and management using tools such as Amazon EC2, RightScale, and Chef. As
one of the more senior engineers on the team, I was also responsible for
creating, documenting, and managing developer workflow/process, as well
as planning and managing software release cycles.

\textbf{Converseon, Inc.}\\
Software Engineer\\
Plymouth, MI\\
July 2010 - June 2011

Worked with a very talented team of developers to build, from the ground
up, a scalable social media CRM. We managed hundreds of millions of
records -- from the Twitter Firehose, to Facebook posts, to message
board conversations -- and delivered it to clients in a manageable way.
The tools we provided allowed clients to analyze social media data and
engage consumers in real-time.

\textbf{MS\&L Digital}\\
Web Applications Developer\\
Ann Arbor, MI\\
May 2005 - July 2010

Developed small, agile, scalable applications for projects on tight
deadlines. Due to the varied nature of scope from project to project,
this required me to employ every skill available to me.

\subsection{Education}\label{education}

Indiana Tech, Computer Science, 2004-2005

\subsection{Links}\label{links}

\begin{itemize}
\tightlist
\item
  \url{https://linkedin.com/in/mattmayers}
\item
  \url{https://github.com/majormajors}
\item
  \url{https://hg.sr.ht/~majors}
\end{itemize}

\subsection{References}\label{references}

Available upon request

\end{document}
